Improving the portuguese hyphenation rules

### 2024-07-01 article/dictionary.tex
fix #48

To establish our gold standard for hyphenation, we will compare the
hyphenations offered by all six dictionaries. First, we will determine the total count
of unique hyphenations across these dictionaries using the script
\texttt{hyphenation\-agreements.sh}.
It's worth noting that certain dictionaries annotate words with a colon (`:') to
indicate potential variations in pronunciation or production.
Particularly, `apparent proparoxytones' might appear marked by this colon sign, indicating 
the possibility of a diphthongs or hiatuses in the word ending.
In Portuguese, words ending in \emph{ea}, \emph{eo}, \emph{ia}, \emph{ie},
\emph{io}, \emph{ua}, \emph{ue}, or \emph{uo}, with the stressed syllable
before these endings, can be considered either paroxytones ending in a rising
diphthong or proparoxytones ending in a hiatus. For instance, words like \emph{his-tó-ri:a}
and \emph{on-du-la-tó-ri:o} are examples of words marked as apparent
proparoxytones, suggesting they could be regarded as paroxytones (\emph{his-tó-ria}
and \emph{on-du-la-tó-rio}) or proparoxytones (\emph{his-tó-ri-a} and
\emph{on-du-la-tó-ri-o}). The script \texttt{hyphenationagreements.sh} 
offers four potential approaches to handle these apparent proparoxytones:
retaining the hyphenations with the colon mark to indicate an apparent proparoxytone; 
selecting only the paroxytone or only the proparoxytone counterpart; or counting both paroxytones and proparoxytones. 
Given the lack of consensus in the literature, our initial approach involves 
counting both hyphenations, and we will detail below how we resolve this issue. 
In our hyphenation dictionary, we have identified \NumberOfAppProp{} words marked as apparent proparoxytones.

>>>>

To establish our gold standard for hyphenation, we will compare the
hyphenations offered by all six dictionaries. First, we will determine the
total count of unique hyphenations across these dictionaries using the script
\texttt{hyphenation\-agreements.sh}. It's worth noting that certain
dictionaries annotate words with a colon (`:') to indicate potential variations
in pronunciation or production. Particularly, `apparent proparoxytones' might
appear marked by this colon sign, indicating the possibility of a diphthongs or
hiatuses in the word ending. In Portuguese, words ending in \emph{-ea},
\emph{-eo}, \emph{-ia}, \emph{-ie}, \emph{-io}, \emph{-ua}, \emph{-ue}, or
\emph{-uo}, with the stressed syllable preceding these endings, are
grammatically considered paroxytones, though they can sometimes be produced as
proparoxytones ending in a hiatus. For instance, words like \emph{his-tó-ri:a}
and \emph{on-du-la-tó-ri:o} are examples of words marked as apparent
proparoxytones, suggesting they could be regarded as paroxytones
(\emph{his-tó-ria} and \emph{on-du-la-tó-rio}) or proparoxytones
(\emph{his-tó-ri-a} and \emph{on-du-la-tó-ri-o}). The script
\texttt{hyphenationagreements.sh} offers four potential approaches to handle
these apparent proparoxytones: retaining the hyphenations with the colon mark
to indicate an apparent proparoxytone; selecting only the paroxytone or only
the proparoxytone counterpart; or counting both paroxytones and proparoxytones.
Given the lack of consensus in the literature, our initial approach involves
counting both hyphenations, and we will detail below how we resolve this issue.
In our hyphenation dictionary, we have identified \NumberOfAppProp{} words
marked as apparent proparoxytones.
